Active Learning from Blackbox to Timed Connectors

### 2016-01-10 paper/paper.tex
.

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% for a smile-face character
\usepackage{wasysym}
% FIXME finally no todos should exist in this draft
\usepackage[textsize=tiny]{todonotes}
% positioning is used for below lef = of
\usetikzlibrary{shapes,arrows,automata,positioning}
% some tikz-styles on reo channels, not required in papers that have nothing to do with Reo

% declaration of environments
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

@@

\title{Active Learning from Blackbox to Timed Connectors}
\author{
\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
\IEEEauthorblockA{
\IEEEauthorrefmark{1}Department of Informatics, School of Mathematical Sciences, Peking University,
Beijing, China\\
liyi\_math@pku.edu.cn, summeng@math.pku.edu.cn
}
}

@@

\subsection{Reo Coordination Language}
\label{sec:reo}
Reo Coordination Language\cite{DBLP:journals/mscs/Arbab04}

@@

\begin{figure}[h]
  \begin{center}
    \input{./images/reoextend.tex}
  \end{center}
  \caption{Merger and Replicator}
  \label{fig:reoextend}
\end{figure}

\subsection{Active Learning and Mealy Machines}

@@

All the following experiments are coded under Golang \emph{1.2.1} and executed on a laptop with 8GB
of RAM and a Core i7-3630 CPU.

\subsection{Case Studies}
\subsection{Performance Optimization}
As a well-known learning algorithm, L* has proved its efficiency in models without time.
However, when dealing with timed connectors, the algorithm failed to meet our expectation.

@@

>>>>

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% for a smile-face character
\usepackage{wasysym}
% listing for codes
\usepackage{listings}

% positioning is used for below lef = of
\usetikzlibrary{shapes,arrows,automata,positioning}
% some tikz-styles on reo channels, not required in papers that have nothing to do with Reo

% FIXME finally no todos should exist in this draft
\usepackage[textsize=tiny]{todonotes}

% -------------------------------------- configurations -----------------------------------------
% declaration of environments
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

@@

% --------------------------------------- information -------------------------------------------
\title{Active Learning from Blackbox to Timed Connectors}
\author{
\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
\IEEEauthorblockA{
\IEEEauthorrefmark{1}Department of Informatics, School of Mathematical Sciences, Peking University,
Beijing, China\\
liyi\_math@pku.edu.cn, summeng@math.pku.edu.cn
}
}

@@

\subsection{Reo Coordination Language}
\label{sec:reo}
Reo is a channel based exogenous coordination language proposed by F. Arbab. in
\cite{DBLP:journals/mscs/Arbab04}. A Reo model, also called \emph{connector}, provides the protocol
that formalizes the communication, synchronization and cooperation among the components which
communicate through the connector. Connectors can be defined with no knowledge of the components,
which makes Reo a powerful ``glue language'' in component-based
development\cite{DBLP:journals/sigsoft/Gill03}.

In Reo, complex connectors are made up of simpler ones, where the atomic connectors are called
\emph{channels}. Each channel has two \emph{channel ends}. There are two type of channel ends:
\emph{source} and \emph{sink}. Source channel ends accepts data into the channel, while sink
channels ends release them out of the channel. Channels are attached on component instances
or \emph{nodes}.

The behavior of some channels are informally described as follows. (Graphical representations
can be found in Figure \ref{fig:basic}).

\begin{itemize}
  \item [-] A \emph{Sync} channel accepts a data item from its source end iff. the data item can be
    dispensed to its sink end simultaneously.
  \item [-] A \emph{LossySync} channel is always prepared to accept data items. These items will be
    send to its sink end simutaneously if possible, otherwise they will be dropped.
  \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
    item through one of its source end iff. a data item is also available for it to simultaneously
    accept through the other end. Then both two data items will be lost.
  \item [-] 
\end{itemize}

@@

\todo{do we need to remove this graph?}
\begin{figure}[h]
  \begin{center}
    \input{./images/reoextend.tex}
  \end{center}
  \caption{Merger and Replicator}
  \label{fig:reoextend}
\end{figure}

\subsection{Mealy Machines}

As an extension of \emph{finite state machine}, Mealy machine was first proposed by George. H. Mealy
in \cite{George1955A}. Compared with other variants, Mealy machines are designed to model
reactive systems, where outputs are determined not only by its current state but also the current
inputs. Besides, Mealy machines are supposed to be \emph{input enabled}, which means that all
possible inputs should be acceptable in all states. In other words, if an input is invalid for some
state, we need to manually use an additional state to describe such exceptions.

As far as we can see, various forms of Mealy machines are defined in different works. In this paper,
we give the formal definition of Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.

\todo{why we choose this version}

\begin{definition}[Mealy machine]
  A Mealy machine is a 6-tuple $(S, s_0, I, O, T, G)$ consisting of the following:
  \begin{itemize}
    \item[-] a finite set of states $S$
    \item[-] a start state (also called initial state) $s_0$ which is an element of $S$
    \item[-] a finite set called the input alphabet $I$
    \item[-] a finite set called the output alphabet $O$
    \item[-] a transition function $\delta : S \times I \rightarrow S$ mapping pairs of a
      state and an input symbol to the corresponding next state.
    \item[-] an output function $\lambda : S \times I \rightarrow O$ mapping pairs
      of a state and an input symbol to the corresponding output symbol.
  \end{itemize}
\end{definition}

\subsection{Active Learning}

@@

All the following experiments are coded under Golang \emph{1.2.1} and executed on a laptop with 8GB
of RAM and a Core i7-3630 CPU. The source code is available at
\url{https://github.com/liyi-david/reo-learn}.

\subsection{Case Studies}

\subsection{Performance Optimization}
As a well-known learning algorithm, L* has proved its efficiency in models without time.
However, when dealing with timed connectors, the algorithm failed to meet our expectation.

@@

\subsection{An Example of the Reo Package}
As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
but also for practical concurrent programming.

\todo{modify the listings package}
\begin{lstlisting}
int main(int argc, char ** argv)
{
  printf(``Hello world!n'');
  return 0;
}
\end{lstlisting}
